---
title: "Paper 3 Appendix 2"
author: "Xiangsen Yang"
date: "4/23/2022"
output:
  pdf_document: default
  html_document: default
---

# Packages required
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(ggplot2)
library(brglm)
library(arm)
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(dplyr)
library(multcomp)
```
# Data 
```{r eval=FALSE, include=TRUE}
cbb <- read.csv("http://stat.lsa.umich.edu/~bbh/s485/data/cbb-mens-2022-03-27.csv")
cbb$Date <- as.Date(cbb$Date)
```
# Fit a plain-vanilla Bradley-Terry model, taking Villanova as reference team
```{r eval=FALSE, include=TRUE}
#Without home-field advantage
#Villanova as reference team
bt_1 <- glm(formula = Home_Win ~ . -Date - Villanova - 1, family = binomial, data = cbb) 
```
# Penalized Logistic Regression, taking Villanova as reference team
```{r eval=FALSE, include=TRUE}
pen_1 <- arm::bayesglm(formula = Home_Win ~ . -Date - Villanova - 1, family = binomial, data = cbb) 
```


# Accounting for game location and season, taking Villanova as reference team
```{r eval=FALSE, include=TRUE}

#Plain-Vanilla"model:
bt_2 <- glm(formula = Home_Win ~ .-Date - Villanova - 1  
                      + I(Date >= as.Date("2022-01-01"))
                      , family = binomial, data = cbb)

#Penalized model:
pen_2 <- arm::bayesglm(formula = Home_Win ~ . -Date - Villanova - 1
                      + I(Date >= as.Date("2022-01-01"))
                      , family = binomial, data = cbb)
```

# Assessing Each Model
Evaluating each model with in-sample MSE, cross-validation, and likelihood ratio tests to evaluate quality of adding an intercept to our models.

```{r eval=FALSE, include=TRUE}
#MSEs
#in-sample
(predict(bt_1, data = cbb) - cbb$Home_Win)^2 %>% mean
(predict(pen_1, data = cbb) - cbb$Home_Win)^2 %>% mean
(predict(bt_2, data = cbb) - cbb$Home_Win)^2 %>% mean
(predict(pen_2, data = cbb) - cbb$Home_Win)^2 %>% mean
```

```{r eval=FALSE, include=TRUE}
# cross validation, we choose 5-fold
folds <- sample(rep(1:5, length.out = nrow(cbb))) # n-fold cross-validation

bt_1_cv_mses <- 1:5
pen_1_cv_mses <- 1:5
bt_2_cv_mses <- 1:5
pen_2_cv_mses <- 1:5


for (fold in 1:5) {
  test.rows <- which(folds == fold)
  train <- cbb[-test.rows,]
  test <- cbb[test.rows,]
  bt_1_cv <- glm(formula = Home_Win ~ . -Date -Villanova -1, family = binomial, data = train)
  pen_1_cv <- arm::bayesglm(formula = Home_Win ~ . -Date -Villanova -1, family = binomial, data = train) 

  bt_2_cv <- glm(formula = Home_Win ~ . -Villanova
                      + I(Date >= as.Date("2022-01-01"))
                      , family = binomial, data = train) 
  
  pen_2_cv <- arm::bayesglm(formula = Home_Win ~ .   -Villanova
                      + I(Date >= as.Date("2022-01-01"))
                      , family = binomial, data = train) 
  
  
#MSEs for 5-fold
  bt_1_cv_mses[fold] <- (predict(bt_1, data = test) - test$Home_Win)^2 %>% mean
  pen_1_cv_mses[fold] <- (predict(pen_1, data = test) - test$Home_Win)^2 %>% mean
  bt_2_cv_mses[fold] <- (predict(bt_2, data = test) - test$Home_Win)^2 %>% mean
  pen_2_cv_mses[fold] <- (predict(pen_2, data = test) - test$Home_Win)^2 %>% mean
  
  
}
```


```{r eval=FALSE, include=TRUE}
#CV MSEs
mean(bt_1_cv_mses) 
mean(pen_1_cv_mses) 
mean(bt_2_cv_mses) 
mean(pen_2_cv_mses)
```

```{r eval=FALSE, include=TRUE}
#Likelihood Ratio Tests
anova(bt_1, bt_2, test ="LRT") # is including the intercept and the course of season a significantly better model? - Likelihood Ratio Test
anova(pen_1, pen_2, test ="LRT") # is including the intercept and the course of season a significantly better model? - Likelihood Ratio Test
```


# Rankings by using preferred model
Rankings will be based on coefficients
```{r eval=FALSE, include=TRUE}
# Top 10
pen_2$coefficients %>% sort(decreasing = T) %>% .[1:10]
# Bottom 5
pen_2$coefficients %>% sort %>% .[1:5]

```

# Difference of Fitted Ability Coefficients
Calculating the confidence interval of each difference in team coefficients
```{r eval=FALSE, include=TRUE}
coef(pen_2)[c("Kansas", "North.Carolina")]
coef(pen_2)[c("Kansas", "Duke")]
glht(pen_2, linfct = c("Kansas - North.Carolina >= 0")) %>% confint()
glht(pen_2, linfct = c("Kansas - Duke >= 0")) %>% confint()

```








